---
title: "spotify_viz_data_processing"
author: "Aleksey Klimchenko"
date: "6/6/2021"
output: html_document
---

```{r libraries}
library(shiny)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
library(tidyverse)
library(OneR)
```

## Import a small subset of the foreign market data to test file creation

```{r load data}
BI_raw.df <- readr::read_csv("./BI.csv")
BI_df = BI_raw.df %>% mutate(market_code = "BI")
CA_raw.df <- readr::read_csv("./CA.csv")
CA_df = CA_raw.df %>% mutate(market_code = "CA")
CH_raw.df <- readr::read_csv("./CH.csv")
CH_df = CH_raw.df %>% mutate(market_code = "CH")
CL_raw.df <- readr::read_csv("./CL.csv")
CL_df = CL_raw.df %>% mutate(market_code = "CL")

```

## Filter for Boxplot

```{r}
BI_df <- filter(BI_df, popularity >=10) %>% arrange(desc(popularity))
```


## Create Boxplot of Popularity vs Followers to test visual for the Shiny App


```{r boxplot}
BI_df %>% mutate( bin=cut_width(popularity, width=10, boundary=0)) %>%
  ggplot( aes(x=bin, y=followers) ) +
  geom_boxplot(color = "black", fill="#1DB954") +
  theme(panel.grid.minor = element_line(colour="white", size=0.5)) +
  theme(panel.grid.major = element_line(colour="#191414", size=0.5)) +
#  theme(panel.background = element_rect(fill = "#191414"))
  scale_y_continuous(trans='log10') +
  xlab("Popularity") +
  ylab("Followers")

```

## Testing joins to see how best to create market info for an artist

```{r}
tmp_df = left_join(BI_df, select(CA_df, c(id, market_code)),
                   by = "id",
                   suffix = c("_BI", "_CA"))
tmp_df

```

## Attempted to create a 'master' artist file that stores all markets that they're in 


```{r}
temp_path <- ".\temp_markets"
for (data in list.files(path = "./temp_markets")){

  # create first df if no data exists yet
  # make new column for market codes

  print(data)

  if(!exists("all_markets")){
    first_code <- tools::file_path_sans_ext(data)     # get market code

    all_markets<-read.csv(data, header=TRUE) %>% 
      mutate(market_codes = first_code)  # assign first market code
    rm(first_code)
  }
  
  # if data exists, then add the new market codes
  else if(exists("all_markets")){
    temp_code <- tools::file_path_sans_ext(data) # new market code

    new_data <- read.csv(data, header=TRUE) %>% mutate(market_codes = c(""))
    head(new_data)
    data_left <- left_join(all_markets, new_data)

    # create vector from old codes, append new codes to each
    old_codes <- data_left$market_codes

    data_left$market_codes <- replace(data_left$market_codes, 
                                      1:length(data_left$market_codes), 
                                      paste(old_codes, temp_code, sep=" "))


    # right join and add the new code to the market_codes vector
    data_right <- right_join(all_markets, new_data)
    old_codes <- data_right$market_codes
    data_right$market_codes <- replace(data_right$market_codes, 
                                      1:length(data_right$market_codes), 
                                      paste(old_codes, temp_code, sep=" "))
    
    # combine into one df    
    all_markets <- bind_rows(data_left, data_right)
    head(all_markets)
    
    rm(data_left)
    rm(new_data)
    rm(data_right)
    rm(temp_code)
    rm(old_codes)
  }
}

write.csv(all_markets, "./all_markets.csv", row.names= FALSE)
rm(all_markets)
```

## Decided instead to create a reference file for all market codes
### This script generated the list of country codes for which we have spotify data

```{r}
Code <- c()
File <- c()
for (data in list.files(path = "./artist_market_data")){
  Code <- append(Codes, tools::file_path_sans_ext(data))
  File <- append(File, basename(data))
  
}

avail_markets <- data.frame(Code, File)
country_df <- readr::read_csv("./country_codes.csv")

spotify_market_codes <- right_join(country_df, avail_markets, by="Code")

write.csv(spotify_market_codes, "./spotify_market_codes.csv", row.names= FALSE)

```

## Filtering and subsetting genre data into a useful size

```{r}
genre_df_raw<-readr::read_csv("./data_by_genres_o.csv")

genre_mode1_df <- genre_df_raw %>% filter(mode == 1) %>% arrange(desc(popularity)) %>% select(genres, popularity)
genre_mode0_df <- genre_df_raw %>% filter(mode == 0) %>% arrange(desc(popularity)) %>% select(genres, popularity)

head(genre_mode1_df, 20)
head(genre_mode0_df, 20)


```

## Plotting the most popular genres

```{r}

head(genre_mode1_df,10) %>%
  ggplot( aes(x=genres, y=popularity) ) +
  geom_bar(stat="identity", fill="#1DB954") +
  theme(panel.grid.minor = element_line(colour="white", size=0.5)) +
  theme(panel.grid.major = element_line(colour="#191414", size=0.5)) +
  xlab("Genres") +
  ylab("Popularity") +
  coord_flip()

head(genre_mode0_df,10) %>%
  ggplot( aes(x=genres, y=popularity) ) +
  geom_bar(stat="identity", fill="#1DB954") +
  theme(panel.grid.minor = element_line(colour="white", size=0.5)) +
  theme(panel.grid.major = element_line(colour="#191414", size=0.5)) +
  xlab("Genres") +
  ylab("Popularity") +
  coord_flip()


```

## Turns out above is useless; will plot histogram of genre count by popularity












